Do syntactic and semantic similarity lead to interference effects?\\ Evidence from self-paced reading and event-related potentials using German

### 2024-11-25 paper/revision2/ResponseToReviewers.tex

Revised version: ``By contrast, Bayes factors provided either no evidence for or even evidence against syntactic interference in both spatiotemporal windows (BF10 $<$ 1.2). Similarly, Bayes factors provided either no evidence for or even evidence against the interaction in both spatio-temporal windows (BF10 $<$ 1.2)."

\textbf{Did the authors change the analyses? Why what was reported as anecdotal evidence under narrow priors is now reported as no evidence or evidence against?}''
\end{quote}
\subsubsection*{Response to R2.7}
Yes, all analyses were changed in the first round of revision. Firstly, the priors were changed (directional priors in the original version and symmetrical priors in the revised version). Secondly, the method to compute Bayes factors was changed (from bridge sampling to Savage-Dickey, see also our Response to E.3). This resulted in small numerical changes of the results, e.g., BF10 = 2.5 in the original analysis decreased to BF10 = 1.2 in the revised analysis. Furthermore in the original version of the manuscript, we were inconsistent in our description of small BFs, i.e., BF10 = 1.2. Since the first revision and in line with \cite{lee2014bayesian}, we now consistently interpret such small BFs as providing no evidence either way.

\subsection*{Comment R2.8}
\begin{quote}
``2. As a side note, on p. 58, the authors conclude that ``the parser searches for a subject that is within the same clause but uses the animacy cue without reference to the clause in which a noun appears." Does this mechanism truly seem plausible to the authors? What would this imply in practice? \textbf{Does it suggest that semantic and syntactic information are entirely encapsulated from each other?} If we were to set aside the issues I raised earlier, this would be one of the paper's central conclusions, yet the authors fail to provide a credible mechanism to support it.''
\end{quote}
\subsubsection*{Response to R2.8}

To clarify the assumed independence of syntactic and semantic processing, we have revised the former section `Relation to other sentence processing accounts', starting on page \pageref{synsem}. We have also renamed the section to `The use of syntactic and semantic information'.
